\tool

### 2018-01-30 paper/paper.tex
Updates to introduction

To solve the tool discovery problem, we developed ~\textit{\tool} to automatically recommend useful tools to software developers. We designed our system to make suggestions by integrating characteristics of peer interactions and concepts from the software engineering industry. We seek to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated our system by recommending a static analysis tool on open source Java projects. We observed the frequency of recommendations made based on developer changes to a code base and also examined how software developers reacted to receiving a suggestion from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel automated recommendation system \tool~ that allows researchers to recommend software development tools to GitHub developers, and
 \item an evaluation of the applicability and usefulness of our approach using the \textsc{Error Prone} static analysis tool
 \end{itemize}

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}.\footnote{http://errorprone.info} \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

>>>>

To help solve the tool discovery problem, we developed \textit{\tool} to automatically recommend useful tools to software developers. We designed our system to make suggestions by integrating characteristics of peer interactions found in previous work as well as concepts from software engineering. \tool contains a unique workflow that runs specific tools and makes customized recommendations to developers on GitHub\footnote{https://github.com}, the most popular code hosting site for collaborative software development. This work seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluate \tool by recommending the \textsc{Error Prone}\footnote{http://errorprone.info} static analysis tool on open source Java GitHub projects. We observed the frequency of recommendations made and examined how software developers reacted to receiving a suggestion from our system. This research makes the following contributions:

\begin{itemize}
 \item a novel automated recommendation system \tool~that allows researchers to recommend software development tools to GitHub developers, and
 \item an evaluation on the applicability and usefulness of our approach using \textsc{Error Prone}
 \end{itemize}

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.
